Compare doublet detection methods

### 2024-05-13 analyses/doublet-detection/01_compare-doublet-methods.Rmd

---
title: "ewings-cell-type Analysis"
author:
  - Your name here
date: "`r Sys.Date()`"
output: html_notebook
---

@@

This a template for an analysis notebook using R Markdown.

It is a good idea to start with a brief introduction to the analysis, including the purpose of the analysis, the data used, and the methods applied.
Replace this text with your own introduction, and be sure to update the `title:` and `author:` fields in the YAML header at the top of the document.

Don't forget to rename this file as well!

@@

Load required packages in the following chunk, if needed.
Do not install packages here; only load them with the `library()` function.

```{r packages}
# load required packages
# e.g. library(tidyverse)
```

You may also want to use the `package::function()` syntax within your code for better tracking of which functions come from which packages, and to avoid conflicts between functions with the same name in different packages.

@@

Setting paths to directories and files for input and output at the start of a notebook can be helpful for organization and reproducibility.
You may not know all of the paths you need when you start a notebook, but once you do, keeping them all in one place is helpful, both for yourself in the future and for other users of the notebook.

@@

In the chunk below, we include some common directories that you might need, finding their locations using the very useful [`rprojroot` package](https://rprojroot.r-lib.org/).

@@

# The path to this module
module_base <- file.path(repository_base, "analyses", "ewings-cell-type")
```

@@

Organize the remainder of your content into sections and subsections as appropriate for your analysis.

Add a new code chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I* on Windows or Linux, *Cmd+Option+I* on a Mac.
Be sure to comment your code and explain your steps as you go.

When you save the notebook, an HTML file containing the code and output will be saved alongside it.
To preview the HTML file, click the *Preview* button or press *Ctrl+Shift+K* on Windows or Linux, *Cmd+Shift+K* on a Mac.

The preview shows you a rendered HTML copy of the contents of the editor.
Consequently, *Preview* does not run any R code chunks.
Instead, the output of the chunk when it was last run in the editor is displayed.

It is usually a good idea to rerun the entire notebook before sharing any output, to ensure that the notebook and output files are fully up to date.
You can do this by clicking on the *Run* menu in the toolbar and clicking on *Restart R and Run All Chunks*.

>>>>

---
title: "Compare doublet detection methods"
author:
  - Stephanie J. Spielman
date: "`r Sys.Date()`"
output: html_notebook
---

@@

This notebook will compare doublet detection results from several methods across a set of ScPCA libraries (_not multiplexed ones_) with varying size and diagnoses. 
The methods include [`scDblFinder`](https://bioconductor.org/packages/3.18/scDblFinder) and three methods from [`scds`](https://bioconductor.org/packages/devel/bioc/vignettes/scds/inst/doc/scds.html): `cxds`, `bsds`, and `hybrid` (a combination of the previous two methods).

@@

```{r packages}
# load required packages
library(SingleCellExperiment)
library(scDblFinder)
library(scds)
```

@@

@@

@@

# The path to this module
module_base <- file.path(repository_base, "analyses", "doublet-detection")
```

@@
